Weather Data Integration and Assimilation System\\

### 2020-02-09 lit/sec_1-fews.tex
Fix: Reference numbers should ideally not be listed with Figure names.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.7\textwidth]{fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
    \caption{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
    \label{fi:fews_schematic}
\end{figure}
\dbc{Most figures are of low quality. You need to make sure figure resolution/quality is not lost. Dot should come after reference no. Fix all places.}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
    \caption{Architecture of \acrshort{fews} % showing the data base, the data access layers and examples of functional modules that communicate through the data access layer. 
    \cite{Werner2013TheSystem} }
    \label{fi:fews_data_layer}
\end{figure}
Most of the library of functions provided work equally on scalar and gridded time series. As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}. As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection. It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible. But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
    \caption{ Linking \acrshort{fews} with external models. The figure shows the flow of data through XML and native model formats using solid lines, while executable commands are shown by dashed lines. \cite{Werner2013TheSystem} }
    \label{fi:fews_general_adapter}
\end{figure}
On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data. This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}. It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step. \acrshort{fews} subsequently imports the results into the database from the XML files (see Fig. \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}. The process is simple and consistence through out all the model integration. The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system. Users does not have the flexibility to run the models with different configurations such as running with parallel execution. That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process. This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system. But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.7\textwidth]{fews/Schematic-structure-of-a-fl-ood-forecasting-system-showing-the-position-of-Delft-FEWS_W640.jpg}
    \caption[Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment]{Schematic structure of a flood forecasting system including \acrshort{fews} and links to other primary systems within the operational environment \cite{Werner2013TheSystem}.}
    \label{fi:fews_schematic}
\end{figure}
\dbc{Most figures are of low quality. You need to make sure figure resolution/quality is not lost. Dot should come after reference no. Fix all places.}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.jpg}\\
    \caption[Architecture of \acrshort{fews}]{Architecture of \acrshort{fews} \cite{Werner2013TheSystem}.}
    \label{fi:fews_data_layer}
\end{figure}
Most of the library of functions provided work equally on scalar and gridded time series. As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}. As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection. It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible. But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.jpg}\\
    \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
    \label{fi:fews_general_adapter}
\end{figure}
On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data. This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}. It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step. \acrshort{fews} subsequently imports the results into the database from the XML files (see Fig. \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}. The process is simple and consistence through out all the model integration. The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system. Users does not have the flexibility to run the models with different configurations such as running with parallel execution. That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process. This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system. But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.

### 2020-02-09 lit/sec_2-lead.tex
Fix: Reference numbers should ideally not be listed with Figure names.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
    \caption{Layered architecture of LEAD. Fundamental capabilities familiar to meteorologists are shown in the top level, next are the tools for enacting these capabilities and the middleware that links everything together. System-generated products appear at the bottom \cite{Droegemeier2005Service-OrientedWeather}. }
    \label{fi:lead_system}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
    \caption{LEAD system framework %. LEAD is composed of several interacting subsystems, with the LEAD grid representing a stable, secure environment for development and testing. 
    \cite{Droegemeier2005Service-OrientedWeather} .}
    \label{fi:lead_framework}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
    \caption{LEAD’s service-oriented architecture %. A wide variety of services and resources, grouped here according to general functionality, comprise the LEAD architecture, including services that cut across all aspects of the system. 
    \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_soa}
\end{figure}

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-Fundamental-capabilities-familiar-to-meteorologists-are-shown-in-the-top_W640.jpg}\\
    \caption[Layered architecture of LEAD]{Layered architecture of LEAD \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_system}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lead/LEAD-system-framework-LEAD-is-composed-of-several-interacting-subsystems-with-the-LEAD_W640.jpg}\\
    \caption[LEAD system framework]{LEAD system framework \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_framework}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{lead/LEADs-service-oriented-architecture-A-wide-variety-of-services-and-resources-grouped_W640.jpg}\\
    \caption[LEAD’s service-oriented architecture]{LEAD’s service-oriented architecture \cite{Droegemeier2005Service-OrientedWeather}.}
    \label{fi:lead_soa}
\end{figure}
